The fundamental shape of dynamic experiences is preserved in episodic memory

### 2018-07-16 main.tex
added corrmats supp fig

Next, we investigated the temporal structure of the recall matrices. For each participant, we computed a timepoint (68 to 294) by timepoint (68 to 294) correlation matrix from the recall models. An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d). Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp Fig X). Notably, this suggests that participants recounted the video in discriminable segments, potentially indexing the recall of specific events from the video.

@@

\bibliography{memlab}
\end{document}

>>>>

Next, we investigated the temporal structure of the recall matrices. For each participant, we computed a timepoint (68 to 294) by timepoint (68 to 294) correlation matrix from the recall models. An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d). Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp Fig.~\ref{fig:corrmats}). Notably, this suggests that participants recounted the video in discriminable segments, potentially indexing the recall of specific events from the video.

@@

\bibliography{memlab}

% Supplemental materials

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/supp1_corrmats.pdf}
\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.  The yellow boxes represent ``events'' identified by a hidden Markov model.}
\label{fig:corrmats}
\end{figure}

\end{document}
